---
title: "ModelTemp - EcoDrought 2"
execute: 
  cache: false
---


**Purpose:** fit hierarchical stream temp model to all EcoDrought data. Estimate random betas independently, then inspect correlations with catchment covariates post-hoc.

**This model uses air temperature and flow data standardized by BASIN**

```{r include=FALSE}
library(tidyverse)
library(R2jags)
library(MCMCvis)
library(loo)
library(HDInterval)
library(scales)
library(ggmcmc)
library(GGally)
library(beepr)
library(lme4)
```

Notes:

* Consider bringing in additional data from NWIS to fill in middle-upper end of catchment size spectrum (Snake: Blackrock, Cache, Granite...bigger rivers? Hoback, Gros Ventre, Greys...where to draw the line?)
* consider putting a prior on flow variables in the JAGS model to deal with missing values (rather than setting NAs to 0, as in line 57)

## Load data


```{r}
dat <- read_csv("data/EcoDrought_FlowTempData_formatted.csv") #%>% 
  # filter(!is.na(tempc_mean)) %>%
  # mutate(rowNum = 1:nrow(.),
  #        # site_code = as.numeric(as.factor(site_name)),
  #        year_code = year - min(year) + 1)

# redo basin and site codes
# dat <- dat %>% arrange(basin, site_name, year, yday)
# sitecodes <- tibble(site_name = unique(dat$site_name), site_code = 1:length(unique(dat$site_name)))
# basincodes <- tibble(basin = unique(dat$basin), basin_code = 1:length(unique(dat$basin)))

# dat <- dat %>%
#   select(-c(site_code, basin_code)) %>% 
#   left_join(sitecodes) %>%
#   # left_join(basincodes) %>%
#   mutate(rowNum = 1:nrow(.))

dat
```

Drop sites without any flow or water temp observations and re-do site and year codes
```{r}
# dropsites <- unlist(dat %>% 
#   group_by(site_name) %>% 
#   summarize(numt = sum(!is.na(tempc_mean)), 
#             numf = sum(!is.na(z_Yield_mm_log))) %>% 
#   ungroup() %>%
#   filter(numt == 0 | numf == 0) %>%
#   select(site_name))
# 
# dat <- dat %>% 
#   filter(!site_name %in% dropsites) %>%
#   mutate(rowNum = 1:nrow(.),
#          site_code = as.numeric(as.factor(site_name)),
#          year_code = year - min(year) + 1)
```

View basins and sites
```{r}
DT::datatable(dat %>% group_by(basin, site_name, site_code) %>% summarise(n = n()) )
```

How much missing data?  *Need to put a prior on flow*
```{r}
sum(is.na(dat$zbas_air_temp_mean))
sum(is.na(dat$zbas_air_temp_mean_lag1))
sum(is.na(dat$zbas_air_temp_mean_lag2))
sum(is.na(dat$zbas_Yield_mm_log))
```

Set covariate NAs to 0. Probably should change this to latent variable in model, especially when expanding to sites where flow data is more rare
```{r}
# dat <- dat %>% mutate(z_air_temp_mean = ifelse(is.na(z_air_temp_mean), 0, z_air_temp_mean),
#                       z_air_temp_mean_lag1 = ifelse(is.na(z_air_temp_mean_lag1), 0, z_air_temp_mean_lag1),
#                       z_air_temp_mean_lag2 = ifelse(is.na(z_air_temp_mean_lag2), 0, z_air_temp_mean_lag2),
#                       z_Yield_mm_log = ifelse(is.na(z_Yield_mm_log), 0, z_Yield_mm_log))
```


View data

::: panel-tabset

#### Distributions
```{r eval=FALSE}
ggpubr::ggarrange(dat %>% ggplot(aes(x = air_temp_mean, color = site_name)) + geom_density() + theme_bw(),
                  dat %>% ggplot(aes(x = flow_mean_log, color = site_name)) + geom_density() + theme_bw(),
                  dat %>% ggplot(aes(x = Yield_mm_log, color = site_name)) + geom_density() + theme_bw(),
                  common.legend = TRUE, legend = "right", ncol = 1)
```

#### Air temp
```{r eval=FALSE}
ggplot(dat, aes(yday, z_air_temp_mean))+
  geom_line(aes(color = factor(year))) +
  facet_grid(year ~ site_name)
```

#### Water temp
```{r eval=FALSE}
ggplot(dat, aes(yday, tempc_mean))+
  geom_line(aes(color = factor(year)))+
  facet_grid(year ~ site_name)
```

#### Flow (log and std)
```{r eval=FALSE}
ggplot(dat, aes(yday, z_Yield_mm_log))+
  geom_line(aes(color = factor(year)))+
  facet_grid(year ~ site_name)
```

#### Tw ~ Ta + F
```{r eval=FALSE}
dat %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

#### Ta ~ F
```{r eval=FALSE}
dat %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

#### Ta ~ yday

```{r eval=FALSE}
dat %>% ggplot(aes(x = z_yday, y = z_air_temp_mean, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

#### F ~ yday
```{r eval=FALSE}
dat %>% filter(z_Yield_mm_log != 0) %>% ggplot(aes(x = z_yday, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

:::


```{r}
ggpairs(dat %>% select(yday, zbas_air_temp_mean, zbas_Yield_mm_log))
```



## Specify JAGS model

Specify hierarchical model following Letcher et al. (2016). MODIFIED:

* add prior on covariates to deal with missing values
* calculate Bayesian R^2 and RMSE
* remove the year trends (same as for Hocking et al 2018)
* add catchment covariate effects on random effects parameters

```{r}
cat("model {

    ###----------------- LIKELIHOOD -----------------###
    
    # Days without an observation on the previous day (first observation in a series)
    # No autoregressive term
    
    for (i in 1:nFirstObsRows){
      temp[firstObsRows[i]] ~ dnorm(stream.mu[firstObsRows[i]], pow(sigma, -2)) 
      stream.mu[firstObsRows[i]] <- trend[firstObsRows[i]]
      trend[firstObsRows[i]] <- #inprod(B.0[], X.0[firstObsRows[i], ]) + 
                                inprod(B.site[site[firstObsRows[i]], ], X.site[firstObsRows[i], ]) #+ 
                                #inprod(B.year[year[firstObsRows[i]], ], X.year[firstObsRows[i], ])
      }
    
    # Days with an observation on the previous dat (all days following the first day)
    # Includes autoregressive term (ar1)
    
    for (i in 1:nEvalRows){ 
      temp[evalRows[i]] ~ dnorm(stream.mu[evalRows[i]], pow(sigma, -2))
      stream.mu[evalRows[i]] <- trend[evalRows[i]] + ar1[site[evalRows[i]]] * (temp[evalRows[i]-1] - trend[ evalRows[i]-1 ])
      trend[evalRows[i]] <- #inprod(B.0[], X.0[evalRows[i], ]) + 
                            inprod(B.site[site[evalRows[i]], ], X.site[evalRows[i], ]) #+ 
                            #inprod(B.year[year[evalRows[i]], ], X.year[evalRows[i], ])
      }
    
    
    # Deal with missing data
    for (i in 1:n){
      for (k in 1:Krandom) {
        X.site[i,k] ~ dnorm(0, pow(1, -2))
      }
    }
    
    # Save log-likelihoods for LOO-CV
    for (i in 1:n) {
      loglik[i] <- logdensity.norm(temp[i], stream.mu[i], pow(sigma, -2))
    }
    
    ###----------------- PRIORS ---------------------###
    
    # ar1, hierarchical by site
    for (i in 1:nsites){
      ar1[i] ~ dnorm(ar1Mean, pow(ar1SD, -2)) T(-1,1)       
    }
    ar1Mean ~ dunif(-1, 1) 
    ar1SD ~ dunif(0, 2)


    # model variance
    sigma ~ dunif(0, 100)
    
    
    # fixed effect coefficients
    # for (k in 1:Kfixed) {
    #   B.0[k] ~ dnorm(0, 0.001)
    #   }
      
    # random effect coefficients (by site)
    for (k in 1:Krandom) {
      sigma.B.site[k] ~ dunif(0, 100)
      #alpha.0[k] ~ dnorm(0, pow(10, -2))
      #alpha.1[k] ~ dnorm(0, pow(10, -2))
      for (i in 1:nsites) {
        B.site[i,k] ~ dnorm(0, pow(sigma.B.site[k], -2))
        #mu.B.site[i,k] <- alpha.0[k] + alpha.1[k] * area[i]
      }
    }
    
    # YEAR EFFECTS
    # for(l in 1:L) {
    #   sigma.b.year[l] ~ dunif(0, 100)
    #   for(t in 1:Ti){
    #     B.year[t, l] ~ dnorm(0, pow(sigma.b.year[l], -2))
    #     }
    #   }
    
    # # YEAR EFFECTS
    # # Priors for random effects of year
    # for (t in 1:Ti) { # Ti years
    #   B.year[t, 1:L] ~ dmnorm(mu.year[ ], tau.B.year[ , ])
    #   }
    #   
    # mu.year[1] <- 0
    # 
    # for (l in 2:L) {
    #   mu.year[l] ~ dnorm(0, 0.0001)
    #   }
    #   
    # # Prior on multivariate normal std deviation
    # tau.B.year[1:L, 1:L] ~ dwish(W.year[ , ], df.year)
    # df.year <- L + 1
    # sigma.B.year[1:L, 1:L] <- inverse(tau.B.year[ , ])
    # for (l in 1:L) {
    #   for (l.prime in 1:L) {
    #     rho.B.year[l, l.prime] <- sigma.B.year[l, l.prime]/sqrt(sigma.B.year[l, l]*sigma.B.year[l.prime, l.prime])
    #     }
    #   sigma.b.year[l] <- sqrt(sigma.B.year[l, l])
    # }
    
    
    ###----------------- DERIVED VALUES -------------###
    #residuals[1] <- 0 # hold the place. Not sure if this is necessary...
    for (i in 1:n) {
      residuals[i] <- temp[i] - stream.mu[i]
    }
    
    # variance of model predictions (fixed + random effects)
    var_fit <- (sd(stream.mu))^2

    # residual variance
    var_res <- (sd(residuals))^2

    # calculate Bayesian R^2
    R2 <- var_fit / (var_fit + var_res)

    # Root mean squared error
    rmse <- sqrt(mean(residuals[]^2))
    
    }", file = "JAGS models/DailyTempModelJAGS_Letcher_hierarchical_modified.txt")
```


## Organize objects

Get first observation indices and check that nFirstRowObs equals the number of unique site-years: **must be TRUE!**
```{r}
# row indices for first observation in each site-year
firstObsRows <- unlist(dat %>% 
  group_by(siteYear) %>%
  summarize(index = rowNum[min(which(!is.na(tempc_mean)))]) %>%
  ungroup() %>% 
  select(index))
nFirstObsRows <- length(firstObsRows)

# does the number of first observations match the number of site years?
nFirstObsRows == length(unique(dat$siteYear))
```

Get row indices for all other observations
```{r}
evalRows <- unlist(dat %>% filter(!rowNum %in% firstObsRows) %>% select(rowNum))
nEvalRows <- length(evalRows)
```

Fixed and random effect data
```{r}
data.fixed <- data.frame(airTempLag1 = dat$zbas_air_temp_mean_lag1,
                         airTempLag2 = dat$zbas_air_temp_mean_lag2) 

data.random <- data.frame(intercept = 1,
                          airTemp = dat$zbas_air_temp_mean, 
                          flow =  dat$zbas_Yield_mm_log,
                          airFlow = dat$zbas_air_temp_mean * dat$zbas_Yield_mm_log,
                          airTempLag1 = dat$zbas_air_temp_mean_lag1,
                          airTempLag2 = dat$zbas_air_temp_mean_lag2
                          # doy = dat$z_yday,
                          # doyFlow = dat$z_yday * dat$z_Yield_mm_log
                          )

data.random.years <- data.frame(intercept.year = rep(1, length.out = dim(data.fixed)[1])#, 
                                #dOY  = dat$yday, 
                                #dOY2 = dat$yday^2,
                                #dOY3 = dat$yday^3
                                )

data.random.covs <- log(dat %>% group_by(site_code) %>% summarize(area_sqmi = unique(area_sqmi)) %>% ungroup() %>% arrange(site_code) %>% pull(area_sqmi))

any(is.na(data.random))
any(is.na(data.fixed))
any(is.na(data.random.years))
any(is.na(data.random.covs))
```

Misc. objects
```{r}
Ti <- length(unique(dat$year))
L <- dim(data.random.years)[2]
W.year <- diag(L)
```

Combine data in list
```{r}
# combine data in a list
jags.data <- list("temp" = dat$tempc_mean,
                  "nFirstObsRows" = nFirstObsRows,
                  "firstObsRows" = firstObsRows,
                  "nEvalRows" = nEvalRows,
                  "evalRows" = evalRows,
                  "X.0" = as.matrix(data.fixed),
                  "X.site" = as.matrix(data.random),
                  "X.year" = as.matrix(data.random.years),
                  "Kfixed" = dim(data.fixed)[2],
                  "Krandom" = dim(data.random)[2],
                  "nsites" = length(unique(dat$site_name)),
                  "Ti" = Ti,
                  "L" = L,
                  "W.year" = W.year,
                  "n" = dim(dat)[1],
                  "year" = dat$year_code,
                  "site" = dat$site_code,
                  "area" = data.random.covs
                  )
```

Parameters to monitor
```{r}
jags.params <- c("residuals",
                 "deviance",
                 "sigma",
                 "B.0",
                 "B.site",
                 "B.year",
                 "rho.B.year",
                 "mu.year",
                 "sigma.b.year",
                 "stream.mu",
                 "ar1" ,
                 "ar1Mean",
                 "ar1SD",
                 "temp",
                 "sigma.B.site",
                 "R2",
                 "rmse",
                 "alpha.0",
                 "alpha.1",
                 "loglik"
                 )
```


## Fit model

~1 hour to run: n.chains = 15, n.thin = 20, n.burnin = 5000, n.iter = 9000 
```{r eval=FALSE}
st <- Sys.time()
fit_ed2 <- jags.parallel(data = jags.data, inits = NULL, parameters.to.save = jags.params, 
                        model.file = "JAGS models/DailyTempModelJAGS_Letcher_hierarchical_modified.txt",
                        n.chains = 15, n.thin = 20, n.burnin = 1000, n.iter = 5000, DIC = TRUE)
Sys.time() - st
```


#### Save model ouput

Save to file
```{r eval=FALSE}
saveRDS(fit_ed2, "Model objects/LetcherTempModel_EcoDrought_hierarchical_fullish_stdbas.RDS")
```

Read in fitted model object
```{r cache=FALSE}
fit_ed2 <- readRDS("Model objects/LetcherTempModel_EcoDrought_hierarchical_fullish_stdbas.RDS")
```

Get MCMC samples and summary
```{r cache=FALSE}
top_mod <- fit_ed2
# generate MCMC samples and store as an array
modelout <- top_mod$BUGSoutput
McmcList <- vector("list", length = dim(modelout$sims.array)[2])
for(i in 1:length(McmcList)) { McmcList[[i]] = as.mcmc(modelout$sims.array[,i,]) }
# rbind MCMC samples from 10 chains 
Mcmcdat <- rbind(McmcList[[1]], McmcList[[2]], McmcList[[3]], McmcList[[4]], McmcList[[5]], McmcList[[6]], McmcList[[7]], McmcList[[8]], McmcList[[9]], McmcList[[10]], McmcList[[11]], McmcList[[12]], McmcList[[13]], McmcList[[14]], McmcList[[15]])
param.summary <- modelout$summary
head(param.summary)
```


#### Check convergence

Any problematic R-hat values (>1.05)?
```{r}
fit_ed2$BUGSoutput$summary[,8][top_mod$BUGSoutput$summary[,8] > 1.05]
```

View traceplots
```{r eval=FALSE}
MCMCtrace(top_mod, ind = TRUE, 
          params = c(#"B.0", 
                     "B.site", 
                     # "B.year", 
                     # "ar1", 
                     # "alpha.0", 
                     # "alpha.1",
                     "sigma"), pdf = FALSE)
```

Convert to ggs object
```{r cache=FALSE}
ggfit <- ggs(as.mcmc(top_mod), keep_original_order = TRUE)
head(ggfit)
```


### LOO-CV

*LOO diagnostics indicates that the model fits the data well.*
```{r cache=FALSE}
loglik <- top_mod$BUGSoutput$sims.list$loglik # extract the log-likelihood estimates for each MCMC sample
rf <- relative_eff(exp(loglik), chain_id = rep(1:15, each = 200))
my_loo <- loo(loglik, r_eff = rf)
my_loo
plot(my_loo)

# badpts <- which(my_loo$diagnostics$pareto_k > 0.7)
```


### Goodness of fit

Format observed and predicted values
```{r}
Mcmcdat <- as_tibble(Mcmcdat)

# subset expected and observed MCMC samples
ppdat_exp <- as.matrix(Mcmcdat[,startsWith(names(Mcmcdat), "stream.mu[")])
ppdat_obs <- as.matrix(Mcmcdat[,startsWith(names(Mcmcdat), "temp[")])
```

Bayesian p-value
```{r}
sum(ppdat_exp > ppdat_obs) / (dim(ppdat_obs)[1]*dim(ppdat_obs)[2])
```

PP-check, global
```{r}
ppdat_obs_mean <- apply(ppdat_obs, 2, mean)
ppdat_exp_mean <- apply(ppdat_exp, 2, mean)
tibble(obs = ppdat_obs_mean, exp = ppdat_exp_mean) %>% 
  ggplot(aes(x = obs, y = exp)) + 
  geom_point(alpha = 0.1) + 
  # geom_smooth(method = "lm") +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Observed") + ylab("Predicted (mean)")
```

PP-check by river and year
```{r fig.height=10, fig.width=10, eval=FALSE}
tibble(obs = ppdat_obs_mean, exp = ppdat_exp_mean, site = dat$site_name, year = dat$year) %>% 
  ggplot(aes(x = obs, y = exp)) + 
  geom_point(alpha = 0.1) + 
  # geom_smooth(method = "lm") +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Observed") + ylab("Predicted (mean)") +
  facet_grid(year ~ site)
```

RMSE
```{r}
mean(unlist(ggfit %>% filter(Parameter == "rmse") %>% select(value)))
ggs_density(ggfit, "rmse") + theme_bw() + theme(panel.grid = element_blank())
```

R-squared
```{r}
mean(unlist(ggfit %>% filter(Parameter == "R2") %>% select(value)))
ggs_density(ggfit, "R2") + theme_bw() + theme(panel.grid = element_blank())
```

Histogram of residuals
```{r}
ggplot() + 
  geom_histogram(aes(x = c(ppdat_obs_mean - ppdat_exp_mean)), color = "black", fill = "grey") + 
  xlab("Residuals") + theme_bw() + theme(panel.grid = element_blank()) + 
  geom_vline(xintercept = 0, color = "red") + xlim(-4,4)
```

Residuals by time (day of year): are we missing something important? Like some time dependent variable (e.g., water source to flow ~~ the transition from snowmelt to groundwater). *Not particularly...although perhaps there is a slight uptick in model variance later in the year*
```{r}
tibble(site_name = dat$site_name, year = dat$year, yday = dat$yday, resid = c(ppdat_obs_mean - ppdat_exp_mean)) %>%
  ggplot(aes(x = yday, y = resid)) +
  geom_point(alpha = 0.1) +
  geom_hline(yintercept = c(0), color = "red") +
  geom_smooth(se = FALSE, linewidth = 1.5) +
  theme_bw() + #theme(panel.grid = element_blank()) +
  xlab("Day of year") + ylab("Residual") +
  #facet_wrap(~site_name) + 
  coord_cartesian(ylim = c(-3,3)) #+ facet_wrap(~year)
```


## Plot model output

```{r}
# myparams <- unique(ggfit$Parameter)
mybasins <- c(dat %>% group_by(site_name) %>% summarize(basin = unique(basin)) %>% arrange(basin) %>% ungroup() %>% pull(basin))
mysites <- c(dat %>% group_by(site_name) %>% summarize(site_code = unique(site_code)) %>% arrange(site_code) %>% ungroup() %>% pull(site_name))
```


### Dot plots

::: panel-tabset

##### Air temp lag 1
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",5]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",5]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Air temp lag 1") +
  theme_bw()
```

##### Air temp lag 2
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",6]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",6]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Air temp lag 2") +
  theme_bw()
```

##### Lag effects correlation
```{r}
tibble(site_name = mysites,
       lag1_mean = ggfit %>%
         filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",5]", sep = "")) %>%
         mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",5]", sep = ""))) %>%
         group_by(Parameter) %>% summarize(lag1_mean = mean(value)) %>% ungroup() %>% pull(lag1_mean),
       lag2_mean = ggfit %>%
         filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",6]", sep = "")) %>%
         mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",6]", sep = ""))) %>%
         group_by(Parameter) %>% summarize(lag2_mean = mean(value)) %>% ungroup() %>% pull(lag2_mean),
       basin = mybasins) %>%
  ggplot(aes(x = lag1_mean, y = lag2_mean, color = basin)) + geom_point() + theme_bw()
```

##### Site intercepts
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",1]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",1]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Intercepts") +
  theme_bw()
```

##### Site slopes - temp
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",2]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Slopes, temperature effect") +
  theme_bw()
```

##### Site slopes - flow
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",3]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Slopes, flow effect") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Site slopes - temp x flow
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",4]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",4]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Slopes, temp-flow interaction") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Autoregressive terms
```{r, fig.width=7, fig.height=7}
ggs_caterpillar(ggfit %>% filter(Parameter %in% paste("ar1[", c(1:jags.data$nsites), "]", sep = "")) %>%
                  mutate(Parameter = factor(Parameter, levels = paste("ar1[", c(1:jags.data$nsites), "]", sep = ""))),
                sort = FALSE) + scale_y_discrete(labels = rev(mysites), limits = rev) + theme_bw() + aes(color = mybasins) + xlab("Autoregressive parameter")
```

##### Year effects (offsets)
```{r eval=FALSE}
ggfit %>%
  filter(Parameter %in% c("B.year[1,1]", "B.year[2,1]", "B.year[3,1]", "B.year[4,1]", "B.year[5,1]",
                          "B.year[6,1]", "B.year[7,1]", "B.year[8,1]", "B.year[9,1]", "B.year[10,1]", 
                          "B.year[11,1]", "B.year[12,1]", "B.year[13,1]", "B.year[14,1]")) %>%
  mutate(Parameter = factor(Parameter, levels = c("B.year[1,1]", "B.year[2,1]", "B.year[3,1]", "B.year[4,1]", "B.year[5,1]",
                          "B.year[6,1]", "B.year[7,1]", "B.year[8,1]", "B.year[9,1]", "B.year[10,1]", 
                          "B.year[11,1]", "B.year[12,1]", "B.year[13,1]", "B.year[14,1]"))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(sort(unique(dat$year))), limits = rev) + 
  ylab("Year effects, offsets to intercepts") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Catchment area effects
```{r eval=FALSE}
ggs_caterpillar(ggfit, family = "alpha.1", sort = FALSE) +
  scale_y_discrete(labels = rev(c("Intercepts", "Temp eff.", "Flow eff.", "Temp-Flow int.")), limits = rev) + 
  ylab("Catchment size effects") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```


:::




### Post-hoc catchment effects

Bring in complete daymet data and summarize catchment covariates
```{r fig.width=8, fig.height=8}
climdf <- read_csv("data/Daymet_daily.csv")

basinvars <- climdf %>% 
  filter(site_name %in% mysites) %>%
  group_by(site_name) %>%
  summarize(swe = mean(swe_kgm2)) %>%
  ungroup() %>%
  left_join(dat %>% group_by(site_name) %>% summarize(basin = unique(basin), area_sqmi = unique(area_sqmi), elev_ft = unique(elev_ft)) %>% ungroup())

ggpairs(basinvars %>% mutate(logarea = log(area_sqmi)) %>% select(basin, swe, logarea, elev_ft), mapping = aes(color = basin))


# ggpubr::ggarrange(climdf %>% filter(site_name == "BigCreekLower") %>% ggplot(aes(x = date, y = swe_kgm2)) + geom_line(),
#                   climdf %>% filter(site_name == "CoalCreekLower") %>% ggplot(aes(x = date, y = swe_kgm2)) + geom_line(),
#                   climdf %>% filter(site_name == "NicolaCreek") %>% ggplot(aes(x = date, y = swe_kgm2)) + geom_line(),
#                   climdf %>% filter(site_name == "McGeeCreekTrib") %>% ggplot(aes(x = date, y = swe_kgm2)) + geom_line(),
#                   ncol = 1)
# 
# climdf %>% filter(site_name == "Avery Brook", year(date) >= 2020) %>% ggplot(aes(x = date, y = daylength_sec)) + geom_line()
```


#### Intercepts

```{r fig.width=9, fig.height=5}
mydf <- ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",1]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",1]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(mean = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
  left_join(basinvars) %>% 
  left_join(dat %>% mutate(month = month(date)) %>% filter(month %in% c(8)) %>% group_by(site_name) %>% summarize(meanSummYield = mean(Yield_mm, na.rm = TRUE))) %>%
  group_by(basin) %>%
  mutate(z_area = scale(log(area_sqmi)), 
         z_elev = scale(elev_ft), 
         z_swe = scale(swe),
         z_yield = scale(meanSummYield)) %>%
  ungroup()

summary(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))
ranef(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))


p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Catchment area (log scale)") + ylab("Intercept (posterior mean)") #+ #ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Elevation (feet)") + ylab("Intercept (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("SWE (10-yr mean)") + ylab("Intercept (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Mean August yield (log scale)") + ylab("Intercept (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend = "top")
```


```{r fig.width=9, fig.height=9}
p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Catchment area (log scale)") + ylab("Intercept (posterior mean)") #+ #ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Elevation (feet)") + ylab("Intercept (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("SWE (10-yr mean)") + ylab("Intercept (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Mean August yield (log scale)") + ylab("Intercept (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend = "top")
```


#### Temp effect
```{r fig.width=9, fig.height=5}
mydf <- ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",2]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(mean = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
  left_join(basinvars) %>% 
  left_join(dat %>% mutate(month = month(date)) %>% filter(month %in% c(8)) %>% group_by(site_name) %>% summarize(meanSummYield = mean(Yield_mm, na.rm = TRUE))) %>%
  group_by(basin) %>%
  mutate(z_area = scale(log(area_sqmi)), 
         z_elev = scale(elev_ft), 
         z_swe = scale(swe),
         z_yield = scale(meanSummYield)) %>%
  ungroup()

summary(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))
ranef(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))


p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Catchment area (log scale)") + ylab("Temp effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Elevation (feet)") + ylab("Temp effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("SWE (10-yr mean)") + ylab("Temp effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Mean August yield (log scale)") + ylab("Temp effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend = "top")
```

```{r fig.width=9, fig.height=9}
p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Catchment area (log scale)") + ylab("Temp effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Elevation (feet)") + ylab("Temp effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("SWE (10-yr mean)") + ylab("Temp effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Mean August yield (log scale)") + ylab("Temp effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1)
```


#### Flow effect

```{r fig.width=9, fig.height=5}
mydf <- ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",3]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(mean = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
  left_join(basinvars) %>% 
  left_join(dat %>% mutate(month = month(date)) %>% filter(month %in% c(8)) %>% group_by(site_name) %>% summarize(meanSummYield = mean(Yield_mm, na.rm = TRUE))) %>%
  group_by(basin) %>%
  mutate(z_area = scale(log(area_sqmi)), 
         z_elev = scale(elev_ft), 
         z_swe = scale(swe),
         z_yield = scale(meanSummYield)) %>%
  ungroup()

summary(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))
ranef(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))


p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Catchment area (log scale)") + ylab("Flow effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Elevation (feet)") + ylab("Flow effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("SWE (10-yr mean)") + ylab("Flow effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Mean August yield (log scale)") + ylab("Flow effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend = "top")
```


```{r fig.width=9, fig.height=9}
p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Catchment area (log scale)") + ylab("Flow effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Elevation (feet)") + ylab("Flow effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("SWE (10-yr mean)") + ylab("Flow effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Mean August yield (log scale)") + ylab("Flow effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1)
```


#### Air temp lagged 1

```{r fig.width=9, fig.height=5}
mydf <- ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",5]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",5]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(mean = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
  left_join(basinvars) %>% 
  left_join(dat %>% mutate(month = month(date)) %>% filter(month %in% c(8)) %>% group_by(site_name) %>% summarize(meanSummYield = mean(Yield_mm, na.rm = TRUE))) %>%
  group_by(basin) %>%
  mutate(z_area = scale(log(area_sqmi)), 
         z_elev = scale(elev_ft), 
         z_swe = scale(swe),
         z_yield = scale(meanSummYield)) %>%
  ungroup()

summary(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))
ranef(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))


p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Catchment area (log scale)") + ylab("AirT lag-1 effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Elevation (feet)") + ylab("AirT lag-1 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("SWE (10-yr mean)") + ylab("AirT lag-1 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Mean August yield (log scale)") + ylab("AirT lag-1 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend = "top")
```

```{r fig.width=9, fig.height=9}
p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Catchment area (log scale)") + ylab("AirT lag-1 effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Elevation (feet)") + ylab("AirT lag-1 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("SWE (10-yr mean)") + ylab("AirT lag-1 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Mean August yield (log scale)") + ylab("AirT lag-1 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1)
```

#### Air temp lagged 2
```{r fig.width=9, fig.height=5}
mydf <- ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",6]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",6]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(mean = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
  left_join(basinvars) %>% 
  left_join(dat %>% mutate(month = month(date)) %>% filter(month %in% c(8)) %>% group_by(site_name) %>% summarize(meanSummYield = mean(Yield_mm, na.rm = TRUE))) %>%
  group_by(basin) %>%
  mutate(z_area = scale(log(area_sqmi)), 
         z_elev = scale(elev_ft), 
         z_swe = scale(swe),
         z_yield = scale(meanSummYield)) %>%
  ungroup()

summary(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))
ranef(lmer(mean ~ z_elev * z_yield + (1 + z_elev * z_yield | basin), data = mydf))


p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Catchment area (log scale)") + ylab("AirT lag-2 effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Elevation (feet)") + ylab("AirT lag-2 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("SWE (10-yr mean)") + ylab("AirT lag-2 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  xlab("Mean August yield (log scale)") + ylab("AirT lag-2 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1, common.legend = TRUE, legend = "top")
```


```{r fig.width=9, fig.height=9}
p1 <- mydf %>%
  ggplot(aes(x = log(area_sqmi), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Catchment area (log scale)") + ylab("AirT lag-2 effect (posterior mean)") #+ ggpubr::stat_cor()

p2 <- mydf %>%
  ggplot(aes(x = elev_ft, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Elevation (feet)") + ylab("AirT lag-2 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p3 <- mydf %>%
  ggplot(aes(x = swe, y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("SWE (10-yr mean)") + ylab("AirT lag-2 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

p4 <- mydf %>%
  ggplot(aes(x = log(meanSummYield), y = mean, color = basin)) +
  geom_smooth(method = "lm") + geom_point() + theme_bw() +
  theme(legend.position = "none") +
  facet_wrap(~basin, scales = "free", ncol = 1) +
  xlab("Mean August yield (log scale)") + ylab("AirT lag-2 effect (posterior mean)") + #ggpubr::stat_cor() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())

ggpubr::ggarrange(p1, p2, p3, p4, nrow = 1)
```

