---
title: "ModelTemp - Snake"
---


**Purpose:** fit hierarchical stream temp model to Snake River data. Random betas by site (intercepts, temp, flow, and TxF interaction) modeled as functions of catchment size

```{r include=FALSE}
library(tidyverse)
library(R2jags)
library(MCMCvis)
library(loo)
library(HDInterval)
library(scales)
library(ggmcmc)
library(GGally)
library(beepr)
library(lme4)
```

Notes:

* Consider bringing in additional data from NWIS to fill in middle-upper end of catchment size spectrum (Snake: Blackrock, Cache, Granite...bigger rivers? Hoback, Gros Ventre, Greys...where to draw the line?)
* consider putting a prior on flow variables in the JAGS model to deal with missing values (rather than setting NAs to 0, as in line 57)

## Load data

Set flow = NA to 0. Probably should change this to latent variable in model, especially when expanding to sites where flow data is more rare
```{r}
dat <- read_csv("data/EcoDrought_FlowTempData_formatted.csv") %>% 
  filter(!is.na(tempc_mean),
         basin %in% c("Snake River")) %>%
  mutate(rowNum = 1:nrow(.),
         # site_code = as.numeric(as.factor(site_name)),
         year_code = year - min(year) + 1)

# redo basin and site codes
dat <- dat %>% arrange(basin, site_name, year, yday)
sitecodes <- tibble(site_name = unique(dat$site_name), site_code = 1:length(unique(dat$site_name)))
# basincodes <- tibble(basin = unique(dat$basin), basin_code = 1:length(unique(dat$basin)))

dat <- dat %>%
  select(-c(site_code, basin_code)) %>% 
  left_join(sitecodes) %>%
  # left_join(basincodes) %>%
  mutate(rowNum = 1:nrow(.))

dat
```

View basins and sites
```{r}
DT::datatable(dat %>% group_by(basin, site_name, site_code) %>% summarise(n = n()) )
```

How much missing data?  *Need to put a prior on flow*
```{r}
sum(is.na(dat$z_air_temp_mean))
sum(is.na(dat$z_air_temp_mean_lag1))
sum(is.na(dat$z_air_temp_mean_lag2))
sum(is.na(dat$z_Yield_mm_log))
```

View data

::: panel-tabset

#### Distributions
```{r}
ggpubr::ggarrange(dat %>% ggplot(aes(x = air_temp_mean, color = site_name)) + geom_density() + theme_bw(),
                  dat %>% ggplot(aes(x = flow_mean_log, color = site_name)) + geom_density() + theme_bw(),
                  dat %>% ggplot(aes(x = Yield_mm_log, color = site_name)) + geom_density() + theme_bw(),
                  common.legend = TRUE, legend = "right", ncol = 1)
```

#### Air temp
```{r}
ggplot(dat, aes(yday, z_air_temp_mean))+
  geom_line(aes(color = factor(year))) +
  facet_grid(year ~ site_name)
```

#### Water temp
```{r}
ggplot(dat, aes(yday, tempc_mean))+
  geom_line(aes(color = factor(year)))+
  facet_grid(year ~ site_name)
```

#### Flow (log and std)
```{r}
ggplot(dat, aes(yday, z_Yield_mm_log))+
  geom_line(aes(color = factor(year)))+
  facet_grid(year ~ site_name)
```

#### Tw ~ Ta + F
```{r}
dat %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

#### Ta ~ F
```{r}
dat %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

#### Ta ~ yday

```{r}
dat %>% ggplot(aes(x = z_yday, y = z_air_temp_mean, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

#### F ~ yday
```{r}
dat %>% filter(z_Yield_mm_log != 0) %>% ggplot(aes(x = z_yday, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

:::


```{r}
ggpairs(dat %>% select(z_yday, z_air_temp_mean, z_Yield_mm_log))
```



## Specify JAGS model

Specify hierarchical model following Letcher et al. (2016). MODIFIED:

* add prior on covariates to deal with missing values
* calculate Bayesian R^2 and RMSE
* remove the year trends (same as for Hocking et al 2018)
* add catchment covariate effects on random effects parameters

```{r}
cat("model {

    ###----------------- LIKELIHOOD -----------------###
    
    # Days without an observation on the previous day (first observation in a series)
    # No autoregressive term
    
    for (i in 1:nFirstObsRows){
      temp[firstObsRows[i]] ~ dnorm(stream.mu[firstObsRows[i]], pow(sigma, -2)) 
      stream.mu[firstObsRows[i]] <- trend[firstObsRows[i]]
      trend[firstObsRows[i]] <- inprod(B.0[], X.0[firstObsRows[i], ]) + 
                                inprod(B.site[site[firstObsRows[i]], ], X.site[firstObsRows[i], ]) + 
                                inprod(B.year[year[firstObsRows[i]], ], X.year[firstObsRows[i], ])
      }
    
    # Days with an observation on the previous dat (all days following the first day)
    # Includes autoregressive term (ar1)
    
    for (i in 1:nEvalRows){ 
      temp[evalRows[i]] ~ dnorm(stream.mu[evalRows[i]], pow(sigma, -2))
      stream.mu[evalRows[i]] <- trend[evalRows[i]] + ar1[site[evalRows[i]]] * (temp[evalRows[i]-1] - trend[ evalRows[i]-1 ])
      trend[evalRows[i]] <- inprod(B.0[], X.0[evalRows[i], ]) + 
                            inprod(B.site[site[evalRows[i]], ], X.site[evalRows[i], ]) + 
                            inprod(B.year[year[evalRows[i]], ], X.year[evalRows[i], ])
      }
    
    
    # Deal with missing data
    for (i in 1:n){
      for (k in 1:Krandom) {
        X.site[i,k] ~ dnorm(0, pow(1, -2))
      }
    }
    
    # Save log-likelihoods for LOO-CV
    for (i in 1:n) {
      loglik[i] <- logdensity.norm(temp[i], stream.mu[i], pow(sigma, -2))
    }
    
    ###----------------- PRIORS ---------------------###
    
    # ar1, hierarchical by site
    for (i in 1:nsites){
      ar1[i] ~ dnorm(ar1Mean, pow(ar1SD, -2)) T(-1,1)       
    }
    ar1Mean ~ dunif(-1, 1) 
    ar1SD ~ dunif(0, 2)


    # model variance
    sigma ~ dunif(0, 100)
    
    
    # fixed effect coefficients
    for (k in 1:Kfixed) {
      B.0[k] ~ dnorm(0, 0.001)
      }
      
    # random effect coefficients (by site)
    for (k in 1:Krandom) {
      sigma.B.site[k] ~ dunif(0, 100)
      alpha.0[k] ~ dnorm(0, pow(10, -2))
      alpha.1[k] ~ dnorm(0, pow(10, -2))
      for (i in 1:nsites) {
        B.site[i,k] ~ dnorm(mu.B.site[i,k], pow(sigma.B.site[k], -2))
        mu.B.site[i,k] <- alpha.0[k] + alpha.1[k] * area[i]
      }
    }
    
    # YEAR EFFECTS
    for(l in 1:L) {
      sigma.b.year[l] ~ dunif(0, 100)
      for(t in 1:Ti){
        B.year[t, l] ~ dnorm(0, pow(sigma.b.year[l], -2))
        }
      }
    
    # # YEAR EFFECTS
    # # Priors for random effects of year
    # for (t in 1:Ti) { # Ti years
    #   B.year[t, 1:L] ~ dmnorm(mu.year[ ], tau.B.year[ , ])
    #   }
    #   
    # mu.year[1] <- 0
    # 
    # for (l in 2:L) {
    #   mu.year[l] ~ dnorm(0, 0.0001)
    #   }
    #   
    # # Prior on multivariate normal std deviation
    # tau.B.year[1:L, 1:L] ~ dwish(W.year[ , ], df.year)
    # df.year <- L + 1
    # sigma.B.year[1:L, 1:L] <- inverse(tau.B.year[ , ])
    # for (l in 1:L) {
    #   for (l.prime in 1:L) {
    #     rho.B.year[l, l.prime] <- sigma.B.year[l, l.prime]/sqrt(sigma.B.year[l, l]*sigma.B.year[l.prime, l.prime])
    #     }
    #   sigma.b.year[l] <- sqrt(sigma.B.year[l, l])
    # }
    
    
    ###----------------- DERIVED VALUES -------------###
    #residuals[1] <- 0 # hold the place. Not sure if this is necessary...
    for (i in 1:n) {
      residuals[i] <- temp[i] - stream.mu[i]
    }
    
    # variance of model predictions (fixed + random effects)
    var_fit <- (sd(stream.mu))^2

    # residual variance
    var_res <- (sd(residuals))^2

    # calculate Bayesian R^2
    R2 <- var_fit / (var_fit + var_res)

    # Root mean squared error
    rmse <- sqrt(mean(residuals[]^2))
    
    }", file = "JAGS models/DailyTempModelJAGS_Letcher_hierarchical_siteeffects.txt")
```



## Organize objects

Get first observation indices and check that nFirstRowObs equals the number of unique site-years: **must be TRUE!**
```{r}
# row indices for first observation in each site-year
firstObsRows <- unlist(dat %>% 
  group_by(siteYear) %>%
  summarize(index = rowNum[min(which(!is.na(tempc_mean)))]) %>%
  ungroup() %>% 
  select(index))
nFirstObsRows <- length(firstObsRows)

# does the number of first observations match the number of site years?
nFirstObsRows == length(unique(dat$siteYear))
```

Get row indices for all other observations
```{r}
evalRows <- unlist(dat %>% filter(!rowNum %in% firstObsRows) %>% select(rowNum))
nEvalRows <- length(evalRows)
```

Fixed and random effect data
```{r}
data.fixed <- data.frame(airTempLag1 = dat$z_air_temp_mean_lag1,
                         airTempLag2 = dat$z_air_temp_mean_lag2) 

data.random <- data.frame(intercept = 1,
                          airTemp = dat$z_air_temp_mean, 
                          flow =  dat$z_Yield_mm_log,
                          airFlow = dat$z_air_temp_mean * dat$z_Yield_mm_log
                          # doy = dat$z_yday,
                          # doyFlow = dat$z_yday * dat$z_Yield_mm_log
                          )

data.random.years <- data.frame(intercept.year = rep(1, length.out = dim(data.fixed)[1])#, 
                                #dOY  = dat$yday, 
                                #dOY2 = dat$yday^2,
                                #dOY3 = dat$yday^3
                                )

data.random.covs <- log(dat %>% group_by(site_code) %>% summarize(area_sqmi = unique(area_sqmi)) %>% ungroup() %>% arrange(site_code) %>% pull(area_sqmi))

any(is.na(data.random))
any(is.na(data.fixed))
any(is.na(data.random.years))
any(is.na(data.random.covs))
```

Misc. objects
```{r}
Ti <- length(unique(dat$year))
L <- dim(data.random.years)[2]
W.year <- diag(L)
```

Combine data in list
```{r}
# combine data in a list
jags.data <- list("temp" = dat$tempc_mean,
                  "nFirstObsRows" = nFirstObsRows,
                  "firstObsRows" = firstObsRows,
                  "nEvalRows" = nEvalRows,
                  "evalRows" = evalRows,
                  "X.0" = as.matrix(data.fixed),
                  "X.site" = as.matrix(data.random),
                  "X.year" = as.matrix(data.random.years),
                  "Kfixed" = dim(data.fixed)[2],
                  "Krandom" = dim(data.random)[2],
                  "nsites" = length(unique(dat$site_name)),
                  "Ti" = Ti,
                  "L" = L,
                  "W.year" = W.year,
                  "n" = dim(dat)[1],
                  "year" = dat$year_code,
                  "site" = dat$site_code,
                  "area" = data.random.covs
                  )
```

Parameters to monitor
```{r}
jags.params <- c("residuals",
                 "deviance",
                 "sigma",
                 "B.0",
                 "B.site",
                 "B.year",
                 "rho.B.year",
                 "mu.year",
                 "sigma.b.year",
                 "stream.mu",
                 "ar1" ,
                 "ar1Mean",
                 "ar1SD",
                 "temp",
                 "sigma.B.site",
                 "R2",
                 "rmse",
                 "alpha.0",
                 "alpha.1",
                 "loglik"
                 )
```


## Fit model

```{r eval=FALSE}
fit_ed <- jags.parallel(data = jags.data, inits = NULL, parameters.to.save = jags.params, 
                        model.file = "JAGS models/DailyTempModelJAGS_Letcher_hierarchical_siteeffects.txt",
                        n.chains = 10, n.thin = 10, n.burnin = 3000, n.iter = 5000, DIC = TRUE)
```


#### Save model ouput

Save to file
```{r eval=FALSE}
saveRDS(fit_ed, "Model objects/LetcherTempModel_EcoDrought_hierarchical.RDS")
```

Read in fitted model object
```{r}
fit_ed <- readRDS("Model objects/LetcherTempModel_EcoDrought_hierarchical.RDS")
```

Get MCMC samples and summary
```{r}
top_mod <- fit_ed
# generate MCMC samples and store as an array
modelout <- top_mod$BUGSoutput
McmcList <- vector("list", length = dim(modelout$sims.array)[2])
for(i in 1:length(McmcList)) { McmcList[[i]] = as.mcmc(modelout$sims.array[,i,]) }
# rbind MCMC samples from 10 chains 
Mcmcdat <- rbind(McmcList[[1]], McmcList[[2]], McmcList[[3]], McmcList[[4]], McmcList[[5]], McmcList[[6]], McmcList[[7]], McmcList[[8]], McmcList[[9]], McmcList[[10]])
param.summary <- modelout$summary
head(param.summary)
```


#### Check convergence

Any problematic R-hat values (>1.05)?
```{r}
top_mod$BUGSoutput$summary[,8][top_mod$BUGSoutput$summary[,8] > 1.05]
```

View traceplots
```{r}
MCMCtrace(top_mod, ind = TRUE, 
          params = c("B.0", "B.site", "B.year", 
                     "ar1", "alpha.0", "alpha.1",
                     "sigma"), pdf = FALSE)
```

Convert to ggs object
```{r}
ggfit <- ggs(as.mcmc(top_mod), keep_original_order = TRUE)
head(ggfit)
```


### LOO-CV

```{r eval=FALSE}
loglik <- top_mod$BUGSoutput$sims.list$loglik # extract the log-likelihood estimates for each MCMC sample
rf <- relative_eff(exp(loglik), chain_id = rep(1:10, each = 200))
my_loo <- loo(loglik, r_eff = rf)
my_loo
plot(my_loo)

badpts <- which(my_loo$diagnostics$pareto_k > 0.7)
```


### Goodness of fit

Format observed and predicted values
```{r}
Mcmcdat <- as_tibble(Mcmcdat)

# subset expected and observed MCMC samples
ppdat_exp <- as.matrix(Mcmcdat[,startsWith(names(Mcmcdat), "stream.mu[")])
ppdat_obs <- as.matrix(Mcmcdat[,startsWith(names(Mcmcdat), "temp[")])
```

Bayesian p-value
```{r}
sum(ppdat_exp > ppdat_obs) / (dim(ppdat_obs)[1]*dim(ppdat_obs)[2])
```

PP-check, global
```{r}
ppdat_obs_mean <- apply(ppdat_obs, 2, mean)
ppdat_exp_mean <- apply(ppdat_exp, 2, mean)
tibble(obs = ppdat_obs_mean, exp = ppdat_exp_mean) %>% 
  ggplot(aes(x = obs, y = exp)) + 
  geom_point(alpha = 0.1) + 
  # geom_smooth(method = "lm") +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Observed") + ylab("Predicted (mean)")
```

PP-check by river and year
```{r fig.height=10, fig.width=10, eval=FALSE}
tibble(obs = ppdat_obs_mean, exp = ppdat_exp_mean, site = dat$site_name, year = dat$year) %>% 
  ggplot(aes(x = obs, y = exp)) + 
  geom_point(alpha = 0.1) + 
  # geom_smooth(method = "lm") +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Observed") + ylab("Predicted (mean)") +
  facet_grid(year ~ site)
```

RMSE
```{r}
mean(unlist(ggfit %>% filter(Parameter == "rmse") %>% select(value)))
ggs_density(ggfit, "rmse") + theme_bw() + theme(panel.grid = element_blank())
```

R-squared
```{r}
mean(unlist(ggfit %>% filter(Parameter == "R2") %>% select(value)))
ggs_density(ggfit, "R2") + theme_bw() + theme(panel.grid = element_blank())
```

Histogram of residuals
```{r}
ggplot() + 
  geom_histogram(aes(x = c(ppdat_obs_mean - ppdat_exp_mean)), color = "black", fill = "grey") + 
  xlab("Residuals") + theme_bw() + theme(panel.grid = element_blank()) + 
  geom_vline(xintercept = 0, color = "red") + xlim(-4,4)
```

Residuals by time: are we missing something important? Like some time dependent variable (e.g., water source to streamflow). 
```{r, eval=FALSE}
tibble(site_name = dat$site_name, year = dat$year, yday = dat$yday, resid = c(ppdat_obs_mean - ppdat_exp_mean)) %>%
  ggplot(aes(x = yday, y = resid)) +
  geom_point(alpha = 0.1) +
  geom_hline(yintercept = c(0), color = "red") +
  geom_smooth(se = FALSE, linewidth = 1.5) +
  theme_bw() + #theme(panel.grid = element_blank()) +
  xlab("Day of year") + ylab("Residual") +
  #facet_wrap(~site_name) + 
  coord_cartesian(ylim = c(-3,3)) #+ facet_wrap(~year)
```


## Plot model output

```{r}
# myparams <- unique(ggfit$Parameter)
mysites <- c(dat %>% group_by(site_name) %>% summarize(site_code = unique(site_code)) %>% arrange(site_code) %>% ungroup() %>% pull(site_name))
```


### Dot plots

::: panel-tabset

##### Fixed effects
```{r}
ggs_caterpillar(ggfit, family = "B.0", sort = FALSE) +
  scale_y_discrete(labels = rev(c("Air temp, lag 1", "Air temp, lag 2")), limits = rev) + 
  ylab("Fixed effects") +
  theme_bw()
```


##### Site intercepts
```{r}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",1]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",1]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  ylab("Intercepts") +
  theme_bw()
```

##### Site slopes - temp
```{r}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",2]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  ylab("Slopes, temperature effect") +
  theme_bw()
```

##### Site slopes - flow
```{r}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",3]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  ylab("Slopes, flow effect") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Site slopes - temp x flow
```{r}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",4]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",4]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  ylab("Slopes, temp-flow interaction") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Autoregressive terms
```{r}
ggs_caterpillar(ggfit %>% filter(Parameter %in% paste("ar1[", c(1:jags.data$nsites), "]", sep = "")) %>%
                  mutate(Parameter = factor(Parameter, levels = paste("ar1[", c(1:jags.data$nsites), "]", sep = ""))),
                sort = FALSE) + scale_y_discrete(labels = rev(mysites), limits = rev) + theme_bw() 
```

##### Year effects (offsets)
```{r}
ggfit %>%
  filter(Parameter %in% paste("B.year[", c(1:jags.data$Ti), ",1]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.year[", c(1:jags.data$Ti), ",1]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(sort(unique(dat$year))), limits = rev) + 
  ylab("Year effects, offsets to intercepts") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Catchment area effects
```{r}
ggs_caterpillar(ggfit, family = "alpha.1", sort = FALSE) +
  scale_y_discrete(labels = rev(c("Intercepts", "Temp eff.", "Flow eff.", "Temp-Flow int.")), limits = rev) + 
  ylab("Catchment size effects") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```


:::



### Marginal efffects

#### Temp-flow by site

Site names and codes
```{r}
sitecodes <- dat %>% group_by(site_name) %>% summarize(site_code = unique(site_code)) %>% ungroup()
sitecodes
```

Plotting function
```{r}
margplot <- function(code) {
  np <- 100
  myriv <- sitecodes$site_name[code]
  x_temp <- seq(from = min(dat$z_air_temp_mean[dat$site_name == myriv], na.rm = TRUE),
                to = max(dat$z_air_temp_mean[dat$site_name == myriv], na.rm = TRUE),
                length.out = np)
  x_flow <- seq(from = min(dat$z_Yield_mm_log[dat$site_name == myriv], na.rm = TRUE),
                to = max(dat$z_Yield_mm_log[dat$site_name == myriv], na.rm = TRUE),
                length.out = np)
  pred_df <- expand_grid(x_temp, x_flow)

  # predict from model
  pred_df$pred <- param.summary[paste("B.site[", code, ",1]", sep = ""),1] + param.summary[paste("B.site[", code, ",2]", sep = ""),1]*pred_df$x_temp + param.summary[paste("B.site[", code, ",3]", sep = ""),1]*pred_df$x_flow + param.summary[paste("B.site[", code, ",4]", sep = ""),1]*pred_df$x_temp*pred_df$x_flow

  # lines 
  p1 <- ggplot(pred_df, aes(x = x_temp, y = pred, color = x_flow, group = x_flow)) +
    geom_line() +
    scale_color_distiller(palette = "BrBG", direction = +1) +
    theme_bw() + theme(panel.grid = element_blank()) +
    labs(color = "Flow") + xlab("Air temperature") + ylab("Water temperature") + ylim(-5,10) #+
    #geom_point(dat %>% filter(site_name == myriv), mapping = aes(x = z_air_temp_mean, y = tempc_mean, group = NA), color = "black", size = 0.2, shape = 16) 
 # heatmap
  p2 <- ggplot(pred_df, aes(x = x_temp, y = x_flow)) +
    geom_tile(aes(fill = pred)) +
    scale_fill_distiller(palette = "Spectral", limits = c(-5,10)) +
    theme_bw() + theme(panel.grid = element_blank()) +
    scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) +
    labs(fill = "Water\ntemp.") + xlab("Air temperature") + ylab("Flow") #+ 
    #geom_point(data = dat %>% filter(site_name == myriv), aes(x = z_air_temp_mean, y = z_Yield_mm_log, color = tempc_mean)) +
    #scale_color_distiller(palette = "Spectral", limits = c(0,20)) 
  # combine
  egg::ggarrange(p1, p2, nrow = 1)
}
```


*Interpretation of these plots (specifically, stream temperature outcome) is complicated by the ~large effects of lagged air temperature variables and temporal autocorrelation*

::: panel-tabset

##### Grizzly Creek
```{r}
margplot(1)
```

##### Grouse Creek
```{r}
margplot(2)
```

##### Leidy Creek Mouth
```{r}
margplot(3)
```

##### NF Spread Creek Lower
```{r}
margplot(4)
```

##### NF Spread Creek Upper
```{r}
margplot(5)
```

##### Pacific Creek
```{r}
margplot(6)
```

##### Rock Creek
```{r}
margplot(7)
```

##### SF Spread Creek Lower
```{r}
margplot(8)
```

##### SF Spread Creek Upper
```{r}
margplot(9)
```

##### Spread Creek Dam
```{r}
margplot(10)
```

:::


#### Site-level effects by covs

```{r}
param.summary[c("alpha.1[1]", "alpha.1[2]", "alpha.1[3]", "alpha.1[4]"),]
```


Are temp and flow effects correlated? *Yes...do we need to model this correlation?*
```{r}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",2]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(tempeff = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
  select(-Parameter) %>%
  left_join(ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",3]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""))) %>%
  group_by(Parameter) %>% 
  summarize(floweff = mean(value)) %>%
  ungroup() %>%
  mutate(site_name = mysites) %>%
    select(-Parameter)) %>%
  left_join(dat %>% group_by(site_name) %>% summarize(basin = unique(basin)) %>% ungroup) %>%
  ggplot(aes(x = tempeff, y = floweff)) + 
  geom_smooth(method = "lm") + geom_point() +
  xlab("Temperature effect") + ylab("Flow effect") +
  theme_bw() + ggpubr::stat_cor(label.y.npc = "bottom")
```

*Note that for these 10 sites, catchment area and elevation are ~correlated*
```{r}
dat %>% group_by(site_name) %>% summarize(area_sqmi = unique(area_sqmi), elev_ft = unique(elev_ft)) %>% ggplot(aes(x = elev_ft, y = log(area_sqmi))) + geom_point() + geom_smooth(method = "lm") + theme_bw() + ggpubr::stat_cor(label.x.npc = "center")
```

For all sites/basins
```{r}
read_csv("data/EcoDrought_FlowTempData_formatted.csv") %>% 
  group_by(site_name, basin) %>%
  summarize(logarea = log(unique(area_sqmi)),
            elev_ft = unique(elev_ft)) %>%
  ggplot(aes(x = elev_ft, y = logarea)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~basin, scales = "free") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  ggpubr::stat_cor()
```


Get parameter estimates
```{r}
temp.pars <- c("B.site[1,2]", "B.site[2,2]", "B.site[3,2]", "B.site[4,2]", "B.site[5,2]", "B.site[6,2]", "B.site[7,2]", "B.site[8,2]", "B.site[9,2]", "B.site[10,2]")
flow.pars <- c("B.site[1,3]", "B.site[2,3]", "B.site[3,3]", "B.site[4,3]", "B.site[5,3]", "B.site[6,3]", "B.site[7,3]", "B.site[8,3]", "B.site[9,3]", "B.site[10,3]")
int.pars <- c("B.site[1,4]", "B.site[2,4]", "B.site[3,4]", "B.site[4,4]", "B.site[5,4]", "B.site[6,4]", "B.site[7,4]", "B.site[8,4]", "B.site[9,4]", "B.site[10,4]")

temp.pars <- paste("B.site[", c(1:jags.data$nsites), ",2]", sep = "")
flow.pars <- paste("B.site[", c(1:jags.data$nsites), ",3]", sep = "")
int.pars <- paste("B.site[", c(1:jags.data$nsites), ",4]", sep = "")
# get mean and 95% credible intervals for random effect parameters
mytib <- sitecodes %>%
  mutate(temp.mean = param.summary[temp.pars,1],
         temp.low = param.summary[temp.pars,3],
         temp.high = param.summary[temp.pars,7],
         flow.mean = param.summary[flow.pars,1],
         flow.low = param.summary[flow.pars,3],
         flow.high = param.summary[flow.pars,7],
         int.mean = param.summary[int.pars,1],
         int.low = param.summary[int.pars,3],
         int.high = param.summary[int.pars,7],
         area_log = jags.data$area
         )
mytib
nsims <- 100
```


Temperature effect: stream temperature sensitivity to air temperature is greater in larger catchments (presumably b/c hillslope/groundwater controls on temp are proportionally much weaker). Also, in larger catchments, water has been exposed to air for longer and thus has had more time to equilibrate with local environmental conditions. But interestingly, no effect of mean summer yield, a proxy for relative groundwater contributions to stream flow. 
```{r}
xseq <- seq(from = min(jags.data$area), to = max(jags.data$area), length.out = nsims)
preds <- matrix(data = NA, nrow = dim(Mcmcdat)[1], ncol = nsims)

for (j in 1:dim(Mcmcdat)[1]) {
  preds[j,] <- unlist(Mcmcdat[j,"alpha.0[2]"]) + unlist(Mcmcdat[j,"alpha.1[2]"])*xseq
}
ymean <- apply(preds, 2, mean)
ylow <- apply(preds, 2, quantile, probs = 0.025)
yhigh <- apply(preds, 2, quantile, probs = 0.975)

ggplot() +
  geom_ribbon(aes(x = xseq, ymin = ylow, ymax = yhigh), fill = "grey") +
  geom_line(aes(x = xseq, y = ymean), color = "black", linewidth = 1, lineend = "round") +
  geom_errorbar(aes(x = mytib$area_log, ymin = mytib$temp.low, ymax = mytib$temp.high), width = 0.1) +
  geom_point(aes(x = mytib$area_log, y = mytib$temp.mean), size = 2, shape = 21, fill = "white") +
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Catchment area (log scale)") + ylab("Temperature effect (posterior mean)")
```

Flow effect: in small catchments, increased flow has a warming effect on stream temperature, whereas in large catchments, increased flow has a cooling effect on stream temperature. In small catchments, where proportional contributions from groundwater to streamflow are relatively high, increased flows during snowmelt/runoff warm stream temperatures as snowmelt temperature is warmer than groundwater temperature (???). But in larger catchments where volumetric groundwater contributions are ~low relative to discharge, increased flows during snowmelt cool stream temps as snowmelt temps are colder than ambient air temperatures (which more strongly influence stream temps relative to smaller streams).
```{r}
xseq <- seq(from = min(jags.data$area), to = max(jags.data$area), length.out = nsims)
preds <- matrix(data = NA, nrow = dim(Mcmcdat)[1], ncol = nsims)

for (j in 1:dim(Mcmcdat)[1]) {
  preds[j,] <- unlist(Mcmcdat[j,"alpha.0[3]"]) + unlist(Mcmcdat[j,"alpha.1[3]"])*xseq
}
ymean <- apply(preds, 2, mean)
ylow <- apply(preds, 2, quantile, probs = 0.025)
yhigh <- apply(preds, 2, quantile, probs = 0.975)

ggplot() +
  geom_ribbon(aes(x = xseq, ymin = ylow, ymax = yhigh), fill = "grey") +
  geom_line(aes(x = xseq, y = ymean), color = "black", linewidth = 1, lineend = "round") +
  geom_errorbar(aes(x = mytib$area_log, ymin = mytib$flow.low, ymax = mytib$flow.high), width = 0.1) +
  geom_point(aes(x = mytib$area_log, y = mytib$flow.mean), size = 2, shape = 21, fill = "white") +
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Catchment area (log scale)") + ylab("Flow effect (posterior mean)")
```

Temp-flow interaction: *not sure what this means...*
```{r}
xseq <- seq(from = min(jags.data$area), to = max(jags.data$area), length.out = nsims)
preds <- matrix(data = NA, nrow = dim(Mcmcdat)[1], ncol = nsims)

for (j in 1:dim(Mcmcdat)[1]) {
  preds[j,] <- unlist(Mcmcdat[j,"alpha.0[4]"]) + unlist(Mcmcdat[j,"alpha.1[4]"])*xseq
}
ymean <- apply(preds, 2, mean)
ylow <- apply(preds, 2, quantile, probs = 0.025)
yhigh <- apply(preds, 2, quantile, probs = 0.975)

ggplot() +
  geom_ribbon(aes(x = xseq, ymin = ylow, ymax = yhigh), fill = "grey") +
  geom_line(aes(x = xseq, y = ymean), color = "black", linewidth = 1, lineend = "round") +
  geom_errorbar(aes(x = mytib$area_log, ymin = mytib$int.low, ymax = mytib$int.high), width = 0.1) +
  geom_point(aes(x = mytib$area_log, y = mytib$int.mean), size = 2, shape = 21, fill = "white") +
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Catchment area (log scale)") + ylab("Temp-Flow interaction (posterior mean)")
```

```{r fig.width=8, fig.height=7}
x_temp <- seq(from = min(dat$z_air_temp_mean), to = max(dat$z_air_temp_mean), length.out = nsims)
x_flow <- seq(from = min(dat$z_Yield_mm_log), to = max(dat$z_Yield_mm_log), length.out = nsims)
pred_df_sm <- expand_grid(x_temp, x_flow)
pred_df_lg <- expand_grid(x_temp, x_flow)

# small basins
te <- param.summary["alpha.0[2]",1] + param.summary["alpha.1[2]",1]*min(jags.data$area)
fe <- param.summary["alpha.0[3]",1] + param.summary["alpha.1[3]",1]*min(jags.data$area)
tfe <- param.summary["alpha.0[4]",1] + param.summary["alpha.1[4]",1]*min(jags.data$area)
pred_df_sm$pred <- te*pred_df_sm$x_temp + fe*pred_df_sm$x_flow + tfe*pred_df_sm$x_temp*pred_df_sm$x_flow
# large basins
te <- param.summary["alpha.0[2]",1] + param.summary["alpha.1[2]",1]*max(jags.data$area)
fe <- param.summary["alpha.0[3]",1] + param.summary["alpha.1[3]",1]*max(jags.data$area)
tfe <- param.summary["alpha.0[4]",1] + param.summary["alpha.1[4]",1]*max(jags.data$area)
pred_df_lg$pred <- te*pred_df_lg$x_temp + fe*pred_df_lg$x_flow + tfe*pred_df_lg$x_temp*pred_df_lg$x_flow

# plot
p1sm <- ggplot(pred_df_sm, aes(x = x_temp, y = pred, color = x_flow, group = x_flow)) +
    geom_line() +
    scale_color_distiller(palette = "BrBG", direction = +1) +
    theme_bw() + theme(panel.grid = element_blank()) +
    labs(color = "Flow") + xlab("Air temperature") + ylab("Water temperature (deviation)") + ylim(-7,7)
p2sm <- ggplot(pred_df_sm, aes(x = x_temp, y = x_flow)) +
    geom_tile(aes(fill = pred)) +
    scale_fill_distiller(palette = "Spectral", limits = c(-7,7)) +
    theme_bw() + theme(panel.grid = element_blank()) +
    scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) +
    labs(fill = "Water\ntemp.\ndev.") + xlab("Air temperature") + ylab("Flow")
# plot
p1lg <- ggplot(pred_df_lg, aes(x = x_temp, y = pred, color = x_flow, group = x_flow)) +
    geom_line() +
    scale_color_distiller(palette = "BrBG", direction = +1) +
    theme_bw() + theme(panel.grid = element_blank()) +
    labs(color = "Flow") + xlab("Air temperature") + ylab("Water temperature (deviation)") + ylim(-7,7)
p2lg <- ggplot(pred_df_lg, aes(x = x_temp, y = x_flow)) +
    geom_tile(aes(fill = pred)) +
    scale_fill_distiller(palette = "Spectral", limits = c(-7,7)) +
    theme_bw() + theme(panel.grid = element_blank()) +
    scale_x_continuous(expand = c(0,0)) + scale_y_continuous(expand = c(0,0)) +
    labs(fill = "Water\ntemp.\ndev.") + xlab("Air temperature") + ylab("Flow")

egg::ggarrange(p1sm, p2sm, p1lg, p2lg, ncol = 2, nrow = 2, labels = c("small", "small", "large", "large"))
```

