---
title: "ModelTemp: EcoD w/ catchment covs"
---


**Purpose:** fit hierarchical stream temp model to all EcoDrought data. Estimate random betas as functions of catchment covariates (elevation), hierarchically by basin.

```{r include=FALSE}
library(tidyverse)
library(R2jags)
library(MCMCvis)
library(loo)
library(HDInterval)
library(scales)
library(ggmcmc)
library(GGally)
library(beepr)
library(RColorBrewer)
```

Notes:

* Consider bringing in additional data from NWIS to fill in middle-upper end of catchment size spectrum (Snake: Blackrock, Cache, Granite...bigger rivers? Hoback, Gros Ventre, Greys...where to draw the line?)


## Load data

Set flow = NA to 0. Probably should change this to latent variable in model, especially when expanding to sites where flow data is more rare
```{r}
dat <- read_csv("data/EcoDrought_FlowTempData_formatted.csv")
```

View basins and sites
```{r}
DT::datatable(dat %>% group_by(basin, site_name, site_code) %>% summarise(n = n()) )
```

How much missing data?  *Need to put a prior on flow*
```{r}
sum(is.na(dat$z_air_temp_mean))
sum(is.na(dat$z_air_temp_mean_lag1))
sum(is.na(dat$z_air_temp_mean_lag2))
sum(is.na(dat$z_Yield_mm_log))
```


### View data

#### Temp-flow correlation

::: panel-tabset

##### West Brook
```{r message=FALSE}
dat %>% filter(basin == "West Brook") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

##### Staunton River
```{r}
dat %>% filter(basin == "Staunton River") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

##### Paine Run
```{r}
dat %>% filter(basin == "Paine Run") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

##### Flathead
```{r}
dat %>% filter(basin == "Flathead") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

##### Yellowstone
```{r}
dat %>% filter(basin == "Yellowstone") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

##### Snake River
```{r}
dat %>% filter(basin == "Snake River") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

##### Donner Blitzen
```{r}
dat %>% filter(basin == "Donner Blitzen") %>% ggplot(aes(x = z_air_temp_mean, y = z_Yield_mm_log, colour = tempc_mean)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw() + ggpubr::stat_cor()
```

:::


#### Tw ~ Ta + F

::: panel-tabset

##### West Brook
```{r}
dat %>% filter(basin == "West Brook") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

##### Staunton River
```{r}
dat %>% filter(basin == "Staunton River") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

##### Paine Run
```{r}
dat %>% filter(basin == "Paine Run") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

##### Flathead
```{r}
dat %>% filter(basin == "Flathead") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

##### Yellowstone
```{r}
dat %>% filter(basin == "Yellowstone") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

##### Snake River
```{r}
dat %>% filter(basin == "Snake River") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

##### Donner Blitzen
```{r}
dat %>% filter(basin == "Donner Blitzen") %>% ggplot(aes(x = z_air_temp_mean, y = tempc_mean, color = z_Yield_mm_log)) + geom_point(size = 0.2) + facet_wrap(~site_name) + theme_bw()
```

:::


#### Pairs plot

```{r}
ggpairs(dat %>% select(yday, z_air_temp_mean, z_Yield_mm_log))
```



## Specify JAGS model

Specify hierarchical model following Letcher et al. (2016). MODIFIED:

* estimate all main parameters hierarchically (intercept, air temp, lagged air temp, flow, and temp-flow interaction effects)
* add prior on covariates to deal with missing values
* calculate Bayesian R^2 and RMSE
* remove the year trends and random effects (same as for Hocking et al 2018)
* add catchment covariate effects on random effects parameters, hierarchical by basin

```{r}
cat("model {

###----------------- LIKELIHOOD -----------------###
    
    # Days without an observation on the previous day (first observation in a series)
    # No autoregressive term
    
    for (i in 1:nFirstObsRows){
      temp[firstObsRows[i]] ~ dnorm(stream.mu[firstObsRows[i]], pow(sigma, -2)) 
      stream.mu[firstObsRows[i]] <- trend[firstObsRows[i]]
      trend[firstObsRows[i]] <- inprod(B.site[site[firstObsRows[i]], ], X.site[firstObsRows[i], ])
      }
    
    # Days with an observation on the previous dat (all days following the first day)
    # Includes autoregressive term (ar1)
    
    for (i in 1:nEvalRows){ 
      temp[evalRows[i]] ~ dnorm(stream.mu[evalRows[i]], pow(sigma, -2))
      stream.mu[evalRows[i]] <- trend[evalRows[i]] + ar1[site[evalRows[i]]] * (temp[evalRows[i]-1] - trend[ evalRows[i]-1 ])
      trend[evalRows[i]] <- inprod(B.site[site[evalRows[i]], ], X.site[evalRows[i], ])
      }
    
    # Prior on covariates to handle missing (flow) data
    for (i in 1:n){
      for (k in 1:Krandom) {
        X.site[i,k] ~ dnorm(0, pow(1, -2))
      }
    }
    
    # Save log-likelihoods for LOO-CV
    for (i in 1:n) {
      loglik[i] <- logdensity.norm(temp[i], stream.mu[i], pow(sigma, -2))
    }
    
    ###----------------- PRIORS ---------------------###
    
    # ar1, hierarchical by site
    for (i in 1:nsites){
      ar1[i] ~ dnorm(ar1Mean, pow(ar1SD, -2)) T(-1,1)       
    }
    ar1Mean ~ dunif(-1, 1) 
    ar1SD ~ dunif(0, 2)


    # model variance
    sigma ~ dunif(0, 100)
    
      
    # random effect coefficients (by site with covariate effects, hierarchical by basin)
    for (k in 1:Krandom) {
      
      # site level regressions
      for (i in 1:nsites) {
        B.site[i,k] ~ dnorm(mu.B.site[i,k], pow(sigma.B.site[k], -2))
        mu.B.site[i,k] <- alpha.0[basin[i],k] + alpha.1[basin[i],k] * elev[i] #+ alpha.2[basin[i],k] * area[i] + alpha.3[basin[i],k] * elev[i] * area[i]
      }
      
      # basin level variation in elevation effects
      for (j in 1:nbasins) {
        alpha.0[j,k] ~ dnorm(mu.alpha.0[k], pow(sigma.alpha.0[k], -2))
        alpha.1[j,k] ~ dnorm(mu.alpha.1[k], pow(sigma.alpha.1[k], -2))
        # alpha.2[j,k] ~ dnorm(mu.alpha.2[k], pow(sigma.alpha.2[k], -2))
        # alpha.3[j,k] ~ dnorm(mu.alpha.3[k], pow(sigma.alpha.3[k], -2))
      }
      
      # hyperpriors: global means and standard deviations
      mu.alpha.0[k] ~ dnorm(0, pow(10, -2))
      mu.alpha.1[k] ~ dnorm(0, pow(10, -2))
      # mu.alpha.2[k] ~ dnorm(0, pow(10, -2))
      # mu.alpha.3[k] ~ dnorm(0, pow(10, -2))
      
      sigma.B.site[k] ~ dunif(0, 100)
      
      sigma.alpha.0[k] ~ dunif(0, 100)
      sigma.alpha.1[k] ~ dunif(0, 100)
      # sigma.alpha.2[k] ~ dunif(0, 100)
      # sigma.alpha.3[k] ~ dunif(0, 100)
    }
    
    
    ###----------------- DERIVED VALUES -------------###
    for (i in 1:n) {
      residuals[i] <- temp[i] - stream.mu[i]
    }
    
    # variance of model predictions (fixed + random effects)
    var_fit <- (sd(stream.mu))^2

    # residual variance
    var_res <- (sd(residuals))^2

    # calculate Bayesian R^2
    R2 <- var_fit / (var_fit + var_res)

    # Root mean squared error
    rmse <- sqrt(mean(residuals[]^2))
    
    }", file = "JAGS models/DailyTempModelJAGS_Letcher_hierarchical_modified_site-basin.txt")
```


## Organize objects

Get first observation indices and check that nFirstRowObs equals the number of unique site-years: **must be TRUE!**
```{r}
# row indices for first observation in each site-year
firstObsRows <- unlist(dat %>% 
  group_by(siteYear) %>%
  summarize(index = rowNum[min(which(!is.na(tempc_mean)))]) %>%
  ungroup() %>% 
  select(index))
nFirstObsRows <- length(firstObsRows)

# does the number of first observations match the number of site years?
nFirstObsRows == length(unique(dat$siteYear))
```

Get row indices for all other observations
```{r}
evalRows <- unlist(dat %>% filter(!rowNum %in% firstObsRows) %>% select(rowNum))
nEvalRows <- length(evalRows)
```

Fixed and random effect data
```{r}
data.random <- data.frame(intercept = 1,
                          airTemp = dat$z_air_temp_mean, 
                          flow =  dat$z_Yield_mm_log,
                          airFlow = dat$z_air_temp_mean * dat$z_Yield_mm_log,
                          airTempLag1 = dat$z_air_temp_mean_lag1,
                          airTempLag2 = dat$z_air_temp_mean_lag2
                          )

# data.random.covs <- log(dat %>% group_by(site_code) %>% summarize(area_sqmi = unique(area_sqmi)) %>% ungroup() %>% arrange(site_code) %>% pull(area_sqmi))
data.random.covs <- dat %>% 
  group_by(site_code) %>% 
  summarize(basin = unique(basin), elev_ft = unique(elev_ft), area_sqmi = unique(area_sqmi)) %>% 
  ungroup() %>%
  group_by(basin) %>%
  mutate(z_elev_ft = c(scale(elev_ft)),
         z_area_sqmi = c(scale(area_sqmi))) %>%
  ungroup() %>% 
  arrange(site_code)

data.random.basins <- dat %>%
  group_by(site_code) %>% 
  summarize(basin_code = unique(basin_code)) %>% 
  ungroup() %>%
  arrange(site_code) %>% 
  pull(basin_code)

any(is.na(data.random))
any(is.na(data.random.covs))
```

Misc. objects
```{r}
# Ti <- length(unique(dat$year))
# L <- dim(data.random.years)[2]
# W.year <- diag(L)
```

Combine data in list
```{r}
# combine data in a list
jags.data <- list("temp" = dat$tempc_mean,
                  "nFirstObsRows" = nFirstObsRows,
                  "firstObsRows" = firstObsRows,
                  "nEvalRows" = nEvalRows,
                  "evalRows" = evalRows,
                  "X.site" = as.matrix(data.random),
                  "Krandom" = dim(data.random)[2],
                  "nsites" = length(unique(dat$site_name)),
                  "nbasins" = length(unique(dat$basin)),
                  "n" = dim(dat)[1],
                  "site" = dat$site_code,
                  "basin" = data.random.basins,
                  "elev" = data.random.covs %>% pull(z_elev_ft)#,
                  #"area" = data.random.covs %>% pull(z_area_sqmi)
                  )
```

Parameters to monitor
```{r}
jags.params <- c("temp", "stream.mu", "sigma",
                 "ar1" , "ar1Mean", "ar1SD",
                 "B.site", "sigma.B.site", 
                 "alpha.0", "mu.alpha.0", "sigma.alpha.0", 
                 "alpha.1", "mu.alpha.1", "sigma.alpha.1",
                 # "alpha.2", "mu.alpha.2", "sigma.alpha.2",
                 # "alpha.3", "mu.alpha.3", "sigma.alpha.3",
                 "residuals", "deviance","R2", "rmse", "loglik"
                 )
```


## Fit model

```{r eval=FALSE}
fit_edcov <- jags.parallel(data = jags.data, inits = NULL, parameters.to.save = jags.params, 
                        model.file = "JAGS models/DailyTempModelJAGS_Letcher_hierarchical_modified_site-basin.txt",
                        n.chains = 10, n.thin = 50, n.burnin = 1000, n.iter = 11000, DIC = TRUE)
```


#### Save model ouput

Save to file
```{r eval=FALSE}
saveRDS(fit_edcov, "Model objects/LetcherTempModel_EcoDrought_hierarchical_full_wCovs_Elev.RDS")
```

Read in fitted model object
```{r cache=FALSE}
fit_edcov <- readRDS("Model objects/LetcherTempModel_EcoDrought_hierarchical_full_wCovs_Elev.RDS")
```

Get MCMC samples and summary
```{r cache=FALSE}
top_mod <- fit_edcov
# generate MCMC samples and store as an array
modelout <- top_mod$BUGSoutput
McmcList <- vector("list", length = dim(modelout$sims.array)[2])
for(i in 1:length(McmcList)) { McmcList[[i]] = coda::as.mcmc(modelout$sims.array[,i,]) }
# rbind MCMC samples from 10 chains 
Mcmcdat <- rbind(McmcList[[1]], McmcList[[2]], McmcList[[3]], McmcList[[4]], McmcList[[5]], McmcList[[6]], McmcList[[7]], McmcList[[8]], McmcList[[9]], McmcList[[10]])
param.summary <- modelout$summary
head(param.summary)
rm(fit_ed)
```


#### Check convergence

Any problematic R-hat values (>1.05)?
```{r}
top_mod$BUGSoutput$summary[,8][top_mod$BUGSoutput$summary[,8] > 1.05]
```

View traceplots
```{r eval=FALSE}
MCMCtrace(top_mod, ind = TRUE, 
          params = c("alpha.0", "alpha.1", "mu.alpha.0", "mu.alpha.1",
                     "sigma", "sigma.alpha.0", "sigma.alpha.1"), pdf = FALSE)
```

Convert to ggs object
```{r cache=FALSE}
ggfit <- ggmcmc::ggs(coda::as.mcmc(top_mod), keep_original_order = TRUE)
head(ggfit)
```


### LOO-CV

*LOO diagnostics indicates that the model generally fits the data well.*
```{r cache=FALSE}
loglik <- top_mod$BUGSoutput$sims.list$loglik # extract the log-likelihood estimates for each MCMC sample
rf <- relative_eff(exp(loglik), chain_id = rep(1:10, each = 200))
my_loo <- loo(loglik, r_eff = rf)
my_loo
plot(my_loo)

# badpts <- which(my_loo$diagnostics$pareto_k > 0.7)
```

### Goodness of fit

Format observed and predicted values
```{r cache=FALSE}
Mcmcdat <- as_tibble(Mcmcdat)

# subset expected and observed MCMC samples
ppdat_exp <- as.matrix(Mcmcdat[,startsWith(names(Mcmcdat), "stream.mu[")])
ppdat_obs <- as.matrix(Mcmcdat[,startsWith(names(Mcmcdat), "temp[")])
```

Bayesian p-value
```{r}
sum(ppdat_exp > ppdat_obs) / (dim(ppdat_obs)[1]*dim(ppdat_obs)[2])
```

PP-check, global
```{r}
ppdat_obs_mean <- apply(ppdat_obs, 2, mean)
ppdat_exp_mean <- apply(ppdat_exp, 2, mean)
tibble(obs = ppdat_obs_mean, exp = ppdat_exp_mean) %>% 
  ggplot(aes(x = obs, y = exp)) + 
  geom_point(alpha = 0.1) + 
  # geom_smooth(method = "lm") +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Observed") + ylab("Predicted (mean)")
```

PP-check by river and year
```{r fig.height=10, fig.width=10, eval=FALSE}
tibble(obs = ppdat_obs_mean, exp = ppdat_exp_mean, site = dat$site_name, year = dat$year) %>% 
  ggplot(aes(x = obs, y = exp)) + 
  geom_point(alpha = 0.1) + 
  # geom_smooth(method = "lm") +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  theme_bw() + theme(panel.grid = element_blank()) +
  xlab("Observed") + ylab("Predicted (mean)") +
  facet_grid(year ~ site)
```

RMSE
```{r}
mean(unlist(ggfit %>% filter(Parameter == "rmse") %>% select(value)))
ggs_density(ggfit, "rmse") + theme_bw() + theme(panel.grid = element_blank())
```

R-squared
```{r}
mean(unlist(ggfit %>% filter(Parameter == "R2") %>% select(value)))
ggs_density(ggfit, "R2") + theme_bw() + theme(panel.grid = element_blank())
```

Histogram of residuals
```{r}
ggplot() + 
  geom_histogram(aes(x = c(ppdat_obs_mean - ppdat_exp_mean)), color = "black", fill = "grey") + 
  xlab("Residuals") + theme_bw() + theme(panel.grid = element_blank()) + 
  geom_vline(xintercept = 0, color = "red") + xlim(-4,4)
```

Residuals by time: are we missing something important? Like some time dependent variable (e.g., water source to streamflow). 
```{r}
tibble(site_name = dat$site_name, yday = dat$yday, resid = c(ppdat_obs_mean - ppdat_exp_mean)) %>%
  ggplot(aes(x = yday, y = resid)) +
  geom_point(alpha = 0.1) +
  geom_hline(yintercept = c(0), color = "red") +
  geom_smooth(se = FALSE, linewidth = 1.5) +
  theme_bw() + #theme(panel.grid = element_blank()) +
  xlab("Day of year") + ylab("Residual") +
  #facet_wrap(~site_name) + 
  coord_cartesian(ylim = c(-3,3))
```


## Plot model output

```{r}
# myparams <- unique(ggfit$Parameter)
mybasins <- c(dat %>% group_by(site_name) %>% summarize(basin = unique(basin)) %>% arrange(basin) %>% ungroup() %>% pull(basin))
mysites <- c(dat %>% group_by(site_name) %>% summarize(site_code = unique(site_code)) %>% arrange(site_code) %>% ungroup() %>% pull(site_name))
```


### Primary Effects

::: panel-tabset

##### Air temp lag 1
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",5]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",5]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Air temp lag 1") +
  theme_bw()
```

##### Air temp lag 2
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",6]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",6]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Air temp lag 2") +
  theme_bw()
```

##### Lag effects correlation
```{r}
tibble(site_name = mysites,
       lag1_mean = ggfit %>%
         filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",5]", sep = "")) %>%
         mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",5]", sep = ""))) %>%
         group_by(Parameter) %>% summarize(lag1_mean = mean(value)) %>% ungroup() %>% pull(lag1_mean),
       lag2_mean = ggfit %>%
         filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",6]", sep = "")) %>%
         mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",6]", sep = ""))) %>%
         group_by(Parameter) %>% summarize(lag2_mean = mean(value)) %>% ungroup() %>% pull(lag2_mean),
       basin = mybasins) %>%
  ggplot(aes(x = lag1_mean, y = lag2_mean, color = basin)) + geom_point() + theme_bw() +
  scale_color_brewer(palette = "Dark2")
```

##### Site intercepts
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",1]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",1]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Intercepts") +
  theme_bw()
```

##### Site slopes - temp
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",2]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Slopes, temperature effect") +
  theme_bw()
```

##### Site slopes - flow
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",3]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Slopes, flow effect") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Site slopes - temp x flow
```{r, fig.width=7, fig.height=7}
ggfit %>%
  filter(Parameter %in% paste("B.site[", c(1:jags.data$nsites), ",4]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("B.site[", c(1:jags.data$nsites), ",4]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  aes(color = mybasins) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_discrete(labels = rev(mysites), limits = rev) + 
  xlab("Slopes, temp-flow interaction") +
  theme_bw() + geom_vline(xintercept = 0, linetype = "dashed")
```

##### Autoregressive terms
```{r, fig.width=7, fig.height=7}
ggs_caterpillar(ggfit %>% filter(Parameter %in% paste("ar1[", c(1:jags.data$nsites), "]", sep = "")) %>%
                  mutate(Parameter = factor(Parameter, levels = paste("ar1[", c(1:jags.data$nsites), "]", sep = ""))),
                sort = FALSE) + scale_y_discrete(labels = rev(mysites), limits = rev) + theme_bw() + aes(color = mybasins) + xlab("Autoregressive parameter") +
  scale_color_brewer(palette = "Dark2")
```

:::


### Secondary Effects

```{r}
mybasin_names <- c(dat %>% group_by(basin_code) %>% summarize(basin = unique(basin)) %>% arrange(basin_code) %>% ungroup() %>% pull(basin))
```

View global effects
```{r}
ggfit %>%
  filter(Parameter %in% paste("mu.alpha.1[", c(1:6), "]", sep = "")) %>%
  mutate(Parameter = factor(Parameter, levels = paste("mu.alpha.1[", c(1:6), "]", sep = ""))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Intercept", "Air temp", "Flow", "Air temp x Flow", "Air temp, lag 1", "Air temp, lag 2")), limits = rev) + 
  xlab("Effect of Elevation") +
  theme_bw() + theme(legend.position = "none") + 
  geom_vline(xintercept = 0, linetype = "dashed")
```

#### Dot plots

::: panel-tabset

##### Intercept
```{r}
ggfit %>%
  filter(Parameter %in% c("mu.alpha.1[1]", paste("alpha.1[", c(1:jags.data$nbasins), ",1]", sep = ""))) %>%
  mutate(Parameter = factor(Parameter, levels = c("mu.alpha.1[1]", paste("alpha.1[", c(1:jags.data$nbasins), ",1]", sep = "")))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Global", mybasin_names)), limits = rev) + 
  xlab("Effect of Elevation on Intercept") +
  theme_bw() + theme(legend.position = "none")
```

##### Air Temp Effect
```{r}
ggfit %>%
  filter(Parameter %in% c("mu.alpha.1[2]", paste("alpha.1[", c(1:jags.data$nbasins), ",2]", sep = ""))) %>%
  mutate(Parameter = factor(Parameter, levels = c("mu.alpha.1[2]", paste("alpha.1[", c(1:jags.data$nbasins), ",2]", sep = "")))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Global", mybasin_names)), limits = rev) + 
  xlab("Effect of Elevation on Air Temp. Effect") +
  theme_bw() + theme(legend.position = "none")
```

##### Flow Effect
```{r}
ggfit %>%
  filter(Parameter %in% c("mu.alpha.1[3]", paste("alpha.1[", c(1:jags.data$nbasins), ",3]", sep = ""))) %>%
  mutate(Parameter = factor(Parameter, levels = c("mu.alpha.1[3]", paste("alpha.1[", c(1:jags.data$nbasins), ",3]", sep = "")))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Global", mybasin_names)), limits = rev) + 
  xlab("Effect of Elevation on Flow Effect") +
  theme_bw() + theme(legend.position = "none")
```

##### Temp-Flow Interaction
```{r}
ggfit %>%
  filter(Parameter %in% c("mu.alpha.1[4]", paste("alpha.1[", c(1:jags.data$nbasins), ",4]", sep = ""))) %>%
  mutate(Parameter = factor(Parameter, levels = c("mu.alpha.1[4]", paste("alpha.1[", c(1:jags.data$nbasins), ",4]", sep = "")))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Global", mybasin_names)), limits = rev) + 
  xlab("Effect of Elevation on Temp-Flow Interaction") +
  theme_bw() + theme(legend.position = "none")
```

##### Air temp Lag 1
```{r}
ggfit %>%
  filter(Parameter %in% c("mu.alpha.1[5]", paste("alpha.1[", c(1:jags.data$nbasins), ",5]", sep = ""))) %>%
  mutate(Parameter = factor(Parameter, levels = c("mu.alpha.1[5]", paste("alpha.1[", c(1:jags.data$nbasins), ",5]", sep = "")))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Global", mybasin_names)), limits = rev) + 
  xlab("Effect of Elevation on Air Temp Lag 1 Effect") +
  theme_bw() + theme(legend.position = "none")
```

##### Air temp Lag 2
```{r}
ggfit %>%
  filter(Parameter %in% c("mu.alpha.1[6]", paste("alpha.1[", c(1:jags.data$nbasins), ",6]", sep = ""))) %>%
  mutate(Parameter = factor(Parameter, levels = c("mu.alpha.1[6]", paste("alpha.1[", c(1:jags.data$nbasins), ",6]", sep = "")))) %>%
  ggs_caterpillar(sort = FALSE) +
  scale_y_discrete(labels = rev(c("Global", mybasin_names)), limits = rev) + 
  xlab("Effect of Elevation on Air Temp Lag 2 Effect") +
  theme_bw() + theme(legend.position = "none")
```

:::


#### Marginal Effects Plots


Effect of elevation on air temperature effect
```{r fig.width=9, fig.height=5}
mycols <- brewer.pal(7, name = "Dark2")

# get site level temperature effects
mytib <- tibble(site_name = mysites,
                basin = mybasins,
                basin_code = jags.data$basin,
                eff_mean = param.summary[paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""),1],
                eff_low = param.summary[paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""),3],
                eff_high = param.summary[paste("B.site[", c(1:jags.data$nsites), ",2]", sep = ""),7],
                z_elev = data.random.covs$z_elev_ft)

mytib %>% ggplot() + geom_point(aes(x = z_elev, y = eff_mean, color = basin)) + scale_color_brewer(palette = "Dark2")

nsims <- 100

# create plotting function
regrplot <- function (i) {
  mytib_sub <- mytib %>% filter(basin_code == i)
  xseq <- seq(from = min(mytib_sub$z_elev), to = max(mytib_sub$z_elev), length.out = nsims)
  preds <- matrix(data = NA, nrow = dim(Mcmcdat)[1], ncol = nsims)
  
  for (j in 1:dim(Mcmcdat)[1]) { 
    preds[j,] <- unlist(Mcmcdat[j,paste("alpha.0[", i,",2]", sep = "")]) + unlist(Mcmcdat[j,paste("alpha.1[", i,",2]", sep = "")])*xseq 
    }
  ymean <- apply(preds, 2, mean)
  ylow <- apply(preds, 2, quantile, probs = 0.025)
  yhigh <- apply(preds, 2, quantile, probs = 0.975)
  
  return(ggplot() +
    geom_ribbon(aes(x = xseq, ymin = ylow, ymax = yhigh), fill = mycols[i], alpha = 0.3) +
    geom_line(aes(x = xseq, y = ymean), color = mycols[i], linewidth = 1.5, lineend = "round") +
    geom_errorbar(aes(x = mytib_sub$z_elev, ymin = mytib_sub$eff_low, ymax = mytib_sub$eff_high), width = 0.1) +
    geom_point(aes(x = mytib_sub$z_elev, y = mytib_sub$eff_mean), size = 2, shape = 21, fill = mycols[i]) +
    theme_classic() +
    xlab("Elevation (std.)") + ylab("Temperature effect") + ggtitle(mybasin_names[i]))
}

# global density plot
p1 <- ggfit %>% filter(Parameter == "mu.alpha.1[2]") %>% 
  ggplot() +
  geom_density(aes(value), fill="gray") +
  labs(title = "Global", x = "Elevation effect", y = "Density")+
  theme_classic()

# combined plot
egg::ggarrange(p1, 
               regrplot(1) + theme(axis.title.x = element_blank()), 
               regrplot(2) + theme(axis.title.x = element_blank(), axis.title.y = element_blank()), 
               regrplot(3) + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
               regrplot(4), 
               regrplot(5) + theme(axis.title.y = element_blank()), 
               regrplot(6) + theme(axis.title.y = element_blank()), 
               regrplot(7) + theme(axis.title.y = element_blank()),
               nrow = 2, ncol = 4)
```



Effect of elevation on flow effect
```{r fig.width=9, fig.height=5}
mycols <- brewer.pal(7, name = "Dark2")

# get site level temperature effects
mytib <- tibble(site_name = mysites,
                basin = mybasins,
                basin_code = jags.data$basin,
                eff_mean = param.summary[paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""),1],
                eff_low = param.summary[paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""),3],
                eff_high = param.summary[paste("B.site[", c(1:jags.data$nsites), ",3]", sep = ""),7],
                z_elev = data.random.covs$z_elev_ft)

mytib %>% ggplot() + geom_point(aes(x = z_elev, y = eff_mean, color = basin)) + scale_color_brewer(palette = "Dark2")

nsims <- 100

# create plotting function
regrplot <- function (i) {
  mytib_sub <- mytib %>% filter(basin_code == i)
  xseq <- seq(from = min(mytib_sub$z_elev), to = max(mytib_sub$z_elev), length.out = nsims)
  preds <- matrix(data = NA, nrow = dim(Mcmcdat)[1], ncol = nsims)
  
  for (j in 1:dim(Mcmcdat)[1]) { 
    preds[j,] <- unlist(Mcmcdat[j,paste("alpha.0[", i,",3]", sep = "")]) + unlist(Mcmcdat[j,paste("alpha.1[", i,",3]", sep = "")])*xseq 
    }
  ymean <- apply(preds, 2, mean)
  ylow <- apply(preds, 2, quantile, probs = 0.025)
  yhigh <- apply(preds, 2, quantile, probs = 0.975)
  
  return(ggplot() +
    geom_ribbon(aes(x = xseq, ymin = ylow, ymax = yhigh), fill = mycols[i], alpha = 0.3) +
    geom_line(aes(x = xseq, y = ymean), color = mycols[i], linewidth = 1.5, lineend = "round") +
    geom_errorbar(aes(x = mytib_sub$z_elev, ymin = mytib_sub$eff_low, ymax = mytib_sub$eff_high), width = 0.1) +
    geom_point(aes(x = mytib_sub$z_elev, y = mytib_sub$eff_mean), size = 2, shape = 21, fill = mycols[i]) +
    theme_classic() +
    xlab("Elevation (std.)") + ylab("Flow effect") + ggtitle(mybasin_names[i]))
}

# global density plot
p1 <- ggfit %>% filter(Parameter == "mu.alpha.1[3]") %>% 
  ggplot() +
  geom_density(aes(value), fill="gray") +
  labs(title = "Global", x = "Elevation effect", y = "Density")+
  theme_classic()

# combined plot
egg::ggarrange(p1, 
               regrplot(1) + theme(axis.title.x = element_blank()), 
               regrplot(2) + theme(axis.title.x = element_blank(), axis.title.y = element_blank()), 
               regrplot(3) + theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
               regrplot(4), 
               regrplot(5) + theme(axis.title.y = element_blank()), 
               regrplot(6) + theme(axis.title.y = element_blank()), 
               regrplot(7) + theme(axis.title.y = element_blank()),
               nrow = 2, ncol = 4)
```